NIRCam Flux Calibration Plan

### 2017-02-10 ms.tex
I added a reference to NGC 188's age.
I changed the title to differentiate it from the STScI cal plan(s). Also added K band specificiation on magnitude.

\title{NIRCam Calibration Plan}

@@

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim < 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode. The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9. This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance moduli $(m- M)_V$ should be an additional 0.14 mag.
\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have solar luminosity and solar spectra. 
\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module). We selected clusters $\lesssim 15\arcmin$
\item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
\item {\bf Visibility} The clusters should be spread out in ecliptic longitude to ensure that at least one is visible during the commissioning period.
\end{itemize}

@@

As a check on the maximum age, I downloaded Dartmouth Isochrones \citep{dotter2008dartmouth} and plotted the color-magnitude diagram in Figure \ref{fig:isochrones}.
At 7 Gyr, the main sequence turnoff begins affecting the selection of stars near solar B-V.
Nearly all open clusters are young ($\lesssim$ 5 Gyr) so this really only affects just NGC 188.

>>>>

\title{NIRCam Flux Calibration Plan}

@@

Our team examined open clusters from the WEBDA database\footnote{https://www.univie.ac.at/webda/webda.html} to find clusters most suitable for flux calibration with solar-like stars.
The parameters under consideration were the the following:
\begin{itemize}
\item {\bf Age:} For the methods to work, the solar-mass stars must be on the main sequence. If we require that a solar mass star have $T_{\rm eff}$ = 5780 +/- 100 K, the cluster would have to be between 0.3 Gyr and 10 Gyr using Dartmouth evolutionary models \citep{dotter2008dartmouth}. Furthermore, the age should be $\lesssim$7 Gyr to avoid main sequence turnoff of near-solar stars.
\item {\bf Extinction} Extinction should be as small as possible to minimize the effects of extinction correction to photometry. Of the clusters found, E(B-V) $\lesssim < 0.1$.
\item {\bf Distance Modulus} The cluster must be distant enough to not saturate NIRCam's wide filters in full frame mode. The most easily saturated filter for G stars is the F090W, which corresponds to a G2~V star of 15.9 in the $K$ band. This means the true distance modulus $(m - M)_0$ should be 12.6 for a solar absolute K=3.28 \citep{binney1998book}.
The longer wavelength wide band filters (F200W, F277W, F356W, and F444W) will not saturate for a true distance modulus larger than 11.8.
If one assumes an extinction of E(B-V) = 0.05 and a Galactic average extinction law \citep{cardelli1989}, the visual distance moduli $(m- M)_V$ should be an additional 0.14 mag.
\item {\bf Metallicity} Ideally, the cluster should have near-solar metallicity so that the solar mass stars have solar luminosity and solar spectra. 
\item {\bf Compactness} The cluster should be relatively compact compared to NIRCam's FOV (2'$\times$2' per module). We selected clusters $\lesssim 15\arcmin$
\item {\bf Ancillary data} The clusters should have ancillary photometry from multiple observatories for cross-calibration. We preferred clusters with 2MASS, WISE and IRAC measurements.
\item {\bf Visibility} The clusters should be spread out in ecliptic longitude to ensure that at least one is visible during the commissioning period.
\end{itemize}

@@

As a check on the maximum age, I downloaded Dartmouth Isochrones \citep{dotter2008dartmouth} and plotted the color-magnitude diagram in Figure \ref{fig:isochrones}.
At 7 Gyr, the main sequence turnoff begins affecting the selection of stars near solar B-V.
Nearly all open clusters are young ($\lesssim$ 5 Gyr) so this really only affects just NGC 188 \citep[7.1 Gyr][]{elsanhoury2016ngc188}.
